Active Learning for Level Set Estimation

### 2013-07-31 ijcai13pres.tex
Fix typo
Many small fixes

\begin{frame}
Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($\*x_t \in D$)
\item<4-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
\item<5-> Update our estimated classification
\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
%\color{black}
%\includegraphics<2>[width=4.45in]{figures/oned_0}
%\includegraphics<3>[width=4.45in]{figures/oned_1_0}
%\includegraphics<4>[width=4.45in]{figures/oned_1_1}
%\includegraphics<5>[width=4.45in]{figures/oned_1_2}
%\includegraphics<6>[width=4.45in]{figures/oned_2_0}
%\includegraphics<7>[width=4.45in]{figures/oned_2_1}
%\includegraphics<8>[width=4.45in]{figures/oned_2_2}
%\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Gaussian processes
\end{center}
\begin{itemize}
\item<1-> \textbf{Nonpaparametric}: impose ``smoothness'' assumptions via kernel $k(\*x, \*x')$
\item<2-> Mean \textbf{and variance} estimates: construct confidence intervals $Q_t(\*x)$
\item<7-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1-2>[draft,width=4in]{figures/voned_0_0}
\color{black}
\includegraphics<3>[width=4in]{figures/voned_0_0}
\includegraphics<4>[width=4in]{figures/voned_0_1}
\includegraphics<5>[width=4in]{figures/voned_0_2}
\includegraphics<6-7>[width=4in]{figures/voned_0_3}
\includegraphics<8>[width=4in]{figures/voned_1_0}
\includegraphics<9>[width=4in]{figures/voned_1_1}
\includegraphics<10>[width=4in]{figures/voned_1_2}
\includegraphics<11>[width=4in]{figures/voned_2_0}
\includegraphics<12>[width=4in]{figures/voned_2_1}
\includegraphics<13>[width=4in]{figures/voned_2_2}
\includegraphics<14>[width=4in]{figures/voned_3_0}
\includegraphics<15>[width=4in]{figures/voned_3_1}
\includegraphics<16>[width=4in]{figures/voned_3_2}
\end{center}
\end{frame}

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<22->{\Large\color{green!70!black}\checkmark}
\uncover<16->{
\begin{itemize}
\item<16-> Pick among the yet unclassified\ldots
\item<17-> \ldots the most ``ambiguous'' point
           \uncover<21->{(max. variance or random also work)}
\end{itemize}}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.7in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.7in]{figures/voned_cl_00}
\includegraphics<5>[width=3.7in]{figures/voned_cl_01}
\includegraphics<6>[width=3.7in]{figures/voned_cl_10}
\includegraphics<7>[width=3.7in]{figures/voned_cl_11}
\includegraphics<8>[width=3.7in]{figures/voned_cl_20}
\includegraphics<9>[width=3.7in]{figures/voned_cl_21}
\includegraphics<10>[width=3.7in]{figures/voned_cl_30}
\includegraphics<11>[width=3.7in]{figures/voned_cl_31}
\includegraphics<12>[width=3.7in]{figures/voned_cl_40}
\includegraphics<13-17>[width=3.7in]{figures/voned_cl_41}
\includegraphics<18>[width=3.7in]{figures/voned_cl_41_amb_0}
\includegraphics<19>[width=3.7in]{figures/voned_cl_41_amb_1}
\includegraphics<20->[width=3.7in]{figures/voned_cl_41_amb_2}
\end{center}
\end{frame}

\section{The LSE algorithm}
\definecolor{c1}{RGB}{255,255,255}
\definecolor{c2}{RGB}{27,161,226}
\definecolor{c6}{RGB}{140,191,38}
\definecolor{c4}{RGB}{240,150,9}
\definecolor{c5}{RGB}{255,255,255}
\definecolor{c3}{RGB}{230,113,184}
%\colorlet{c1}{cyan}
%\colorlet{c2}{magenta}
%\colorlet{c3}{red}
%\colorlet{c4}{green}
%\colorlet{c5}{yellow}

\begin{frame}
\begin{columns}[t]
\column{0.45\textwidth}
{\footnotesize
\begin{algorithmic}
  \REQUIRE sample set $D$, GP prior ($\mu_0$, $k$, $\sigma_0$),\\
           \hspace{2.2em}thr. value $h$, accuracy parameter $\epsilon$
  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
  \uncover<2->{
  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
  %\LET{$L_0$}{$\varnothing$}
  %\LET{$U_0$}{$D$}
  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
  \CLET{c1}{$t$}{1}
  }
  \uncover<3->{
  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
    }
    %\LET{$H_t$}{$H_{t-1}$}
    %\LET{$L_t$}{$L_{t-1}$}
    %\LET{$U_t$}{$U_{t-1}$}
    \uncover<4->{
    \CFORALL{c2}{$\*x \in U_{t-1}$}
      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
      \CENDIF{c2} \label{lin:class2}
    \CENDFOR{c2}
    }
    \uncover<5->{
    \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
    }
    \uncover<6->{
    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, $\forall\*x \in U_t$ \label{lin:inf}
    }
    \uncover<3->{
    \CLET{c6}{$t$}{$t + 1$}
  \CENDWHILE{c6}
  }
  \uncover<2->{
  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
  }
\end{algorithmic}
}
\column{0.55\textwidth}
\begin{center}
The Level Set Estimation (\acl) algorithm
\end{center}
\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
\only<6>{$\leftarrow$ {\small update GP estimate}}
\only<7->{
\vspace{3pt}
\begin{itemize}
\only<7->{
\item Monotonicity of
\begin{enumerate}
\item confidence intervals
\item classification
\end{enumerate}
}
\vspace{0em}
\only<8->{
\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
      (trades off sampling cost for accuracy)
}
\end{itemize}
}
\begin{center}
\includegraphics<8->[width=2.5in]{figures/voned_cl_41_eps}
\end{center}
\end{columns}
\end{frame}

@@

\begin{frame}
\begin{theorem}[Simplified]
If we choose $\beta_t$ large enough, then:
\begin{itemize}
\item<2-> \acl terminates after a number of iterations $T$
\begin{enumerate}
\item<3-> smoother kernel $\Rightarrow T \downarrow$
\item<4-> $\sigma \uparrow\ \Rightarrow T \uparrow$
\item<5-> ${\color<7>{red}\epsilon} \uparrow\ \Rightarrow T \downarrow$
\end{enumerate}
\item<6-> The solution returned is {\color<7>{red}$\epsilon$}-accurate with high probability
\end{itemize}
\end{theorem}
\end{frame}

@@

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
%\color{white}
%\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
%\color{black}
%\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
%\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
%\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
%\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
%\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Implicit threshold level
\end{center}
\begin{itemize}
\item<1-> What if we don't know the threshold level $h$?
\vspace{1em}
\item<2-> Implicitly define $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\vspace{1em}
\item<3-> No existing algorithms for this problem (to our knowledge)
\vspace{1em}
\item<4-> We extend \acl (and its theory!) to this setting
\vspace{1em}
\item<5->\textbf{\iacl} algorithm:
\begin{itemize}
\item<6-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
\item<7-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
\end{itemize}
\end{itemize}
\begin{center}
%\color{white}
%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
%\color{black}
%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

\hspace{-1.9em}
\color{white}
\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
\color{black}
\includegraphics<2>[width=3.78in]{figures/limno_bgape_imp_class_0}
\includegraphics<3>[width=3.78in]{figures/limno_bgape_imp_class_20}
\includegraphics<4>[width=3.78in]{figures/limno_bgape_imp_class_40}
\includegraphics<5>[width=3.78in]{figures/limno_bgape_imp_class_60}
\includegraphics<6>[width=3.78in]{figures/limno_bgape_imp_class_80}
\includegraphics<7>[width=3.78in]{figures/limno_bgape_imp_class_100}
\includegraphics<8>[width=3.78in]{figures/limno_bgape_imp_class_120}
\includegraphics<9>[width=3.78in]{figures/limno_bgape_imp_class_140}
\includegraphics<10>[width=3.78in]{figures/limno_bgape_imp_class_160}
\includegraphics<11>[width=3.78in]{figures/limno_bgape_imp_class_180}
\includegraphics<12>[width=3.78in]{figures/limno_bgape_imp_class_200}
\includegraphics<13>[width=3.78in]{figures/limno_bgape_imp_class_340}
\includegraphics<14->[width=3.78in]{figures/limno_bgape_imp_class_486}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Come to the poster session for more\ldots
\end{center}
\begin{itemize}
\item<2-> \ldots theory: sample complexity bounds in more detail
\item<3-> \ldots applications: estimate world regions of low internet latency\\[0.5em]
\hspace{3em}\includegraphics[height=2in]{figures/map}
\item<4-> \ldots results: why does \acl greatly outperform ``straddle'' in some cases?
\end{itemize}
\end{frame}
%\begin{itemize}
%\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
%      for video chatting, online gaming, etc.?
%\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
%\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1-2>[draft,height=2.5in]{figures/map}
%\color{black}
%\includegraphics<3>[height=2.5in]{figures/map}
%\includegraphics<4>[height=2.5in]{figures/map_ls_150}
%\end{center}

>>>>

\begin{frame}
Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($\*x_t \in D$)
\item<4-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
\item<5-> Update our classification estimate
\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
%\color{black}
%\includegraphics<2>[width=4.45in]{figures/oned_0}
%\includegraphics<3>[width=4.45in]{figures/oned_1_0}
%\includegraphics<4>[width=4.45in]{figures/oned_1_1}
%\includegraphics<5>[width=4.45in]{figures/oned_1_2}
%\includegraphics<6>[width=4.45in]{figures/oned_2_0}
%\includegraphics<7>[width=4.45in]{figures/oned_2_1}
%\includegraphics<8>[width=4.45in]{figures/oned_2_2}
%\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Gaussian processes
\end{center}
\begin{itemize}
\item<1-> Mean \textbf{and variance} estimates: construct confidence intervals $C(\*x)$
\item<2-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
\item<3-> Impose prior ``smoothness'' assumptions via kernel $k(\*x, \*x')$
\end{itemize}
\begin{center}
%\color{white}
%\includegraphics<1>[draft,width=4in]{figures/voned_0_0}
%\color{black}
%\includegraphics<1>[width=4in]{figures/voned_0_0}
%\includegraphics<4>[width=4in]{figures/voned_0_1}
%\includegraphics<5>[width=4in]{figures/voned_0_2}
\includegraphics<1-3>[width=4in]{figures/voned_0_3}
%\includegraphics<4>[width=4in]{figures/voned_1_0}
\includegraphics<4>[width=4in]{figures/voned_1_1}
\includegraphics<5>[width=4in]{figures/voned_1_2}
%\includegraphics<7>[width=4in]{figures/voned_2_0}
\includegraphics<6>[width=4in]{figures/voned_2_1}
\includegraphics<7>[width=4in]{figures/voned_2_2}
%\includegraphics<10>[width=4in]{figures/voned_3_0}
\includegraphics<8>[width=4in]{figures/voned_3_1}
\includegraphics<9>[width=4in]{figures/voned_3_2}
\end{center}
\end{frame}

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<19>{\Large\color{green!70!black}\checkmark}
\uncover<16->{
\begin{itemize}
\item<16-> Pick among the yet unclassified\ldots
\item<17-> \ldots the most ``ambiguous'' point
           %\uncover<21->{(max. variance or random also work)}
\end{itemize}}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.7in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.7in]{figures/voned_cl_00}
\includegraphics<5>[width=3.7in]{figures/voned_cl_01}
\includegraphics<6>[width=3.7in]{figures/voned_cl_10}
\includegraphics<7>[width=3.7in]{figures/voned_cl_11}
\includegraphics<8>[width=3.7in]{figures/voned_cl_20}
\includegraphics<9>[width=3.7in]{figures/voned_cl_21}
\includegraphics<10>[width=3.7in]{figures/voned_cl_30}
\includegraphics<11>[width=3.7in]{figures/voned_cl_31}
\includegraphics<12>[width=3.7in]{figures/voned_cl_40}
\includegraphics<13-17>[width=3.7in]{figures/voned_cl_41}
\includegraphics<18->[width=3.7in]{figures/voned_cl_41_amb_2}
\end{center}
\end{frame}

\section{The LSE algorithm}
\definecolor{c1}{RGB}{255,255,255}
\definecolor{c2}{RGB}{27,161,226}
\definecolor{c6}{RGB}{140,191,38}
\definecolor{c4}{RGB}{240,150,9}
\definecolor{c5}{RGB}{240,230,60}
\definecolor{c3}{RGB}{230,113,184}
\definecolor{cwhite}{RGB}{255,255,255}
%\colorlet{c1}{cyan}
%\colorlet{c2}{magenta}
%\colorlet{c3}{red}
%\colorlet{c4}{green}
%\colorlet{c5}{yellow}

\begin{frame}
\begin{columns}[t]
\column{0.55\textwidth}
\begin{center}
The Level Set Estimation (\acl) algorithm
\end{center}
\vspace{5pt}
{\footnotesize
\begin{algorithmic}
  \REQUIRE sample space $D$, threshold level $h$
  \ENSURE predicted super- and sublevel sets
  \STATE
  %\uncover<2->{
  %\CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
  %\LET{$L_0$}{$\varnothing$}
  %\LET{$U_0$}{$D$}
  %\CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
  %\CLET{c1}{$t$}{1}
  %}
  \uncover<2->{
  \CWHILE{cwhite}{$\exists$ unclassified points in $D$}
    %\CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
    }
    %\LET{$H_t$}{$H_{t-1}$}
    %\LET{$L_t$}{$L_{t-1}$}
    %\LET{$U_t$}{$U_{t-1}$}
    \uncover<3->{
    \CFORALL{cwhite}{unclassified points $\*x\in D$}
      \CIF{c2}{$C_t(\*x)$ lies above $h$}
        \CSTATE{c2}classify $\*x$ into superlevel set
      \CELSIF{c2}{$C_t(\*x)$ lies below $h$}
        \CSTATE{c2}classify $\*x$ into sublevel set
      \CELSE
        \CSTATE{c2}leave $\*x$ unclassified
      \CENDIF{c2} \label{lin:class2}
    \CENDFOR{cwhite}
    }
    \uncover<4->{
    \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
    }
    \uncover<5->{
    \CSTATE{c4}perform GP inference
    }
    \uncover<2->{
    %\CLET{c6}{$t$}{$t + 1$}
  \CENDWHILE{cwhite}
  }
  %\uncover<2->{
  %\CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
  %\CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
  %}
\end{algorithmic}
\vspace{30pt}
}
\column{0.45\textwidth}
{\only<3-5>{\begin{center}\end{center}\vspace{83pt}}
%\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
\only<3-5>{$\leftarrow$ {\small classify\\}\vspace{39pt}}
\only<4-5>{$\leftarrow$ {\small sample\\}}
%\only<6>{$\leftarrow$ {\small update GP estimate}}
\only<6->{
\vspace{15pt}
\begin{itemize}
\only<6->{
\item Monotonicity of
\begin{enumerate}
\item confidence intervals
\item classification
\end{enumerate}
}
\vspace{10pt}
\only<7->{
\item Relax classification rules by an accuracy parameter $\epsilon$
}
\end{itemize}
}
\vspace{-20pt}
\begin{center}
\includegraphics<7->[width=2.2in]{figures/voned_cl_41_amb_2}
\end{center}
}
\end{columns}
\end{frame}

@@

\begin{frame}
\begin{theorem}[Simplified]
If we choose $\beta$ appropriately (large enough), then:
\begin{itemize}
\item<2-> \acl terminates after a number of iterations $T$
\begin{enumerate}
\item<3-> smoother kernel $\Rightarrow T \downarrow$
\item<4-> $\sigma \uparrow\ \Rightarrow T \uparrow$
\item<5-> ${\color<7>{red}\epsilon} \uparrow\ \Rightarrow T \downarrow$
\end{enumerate}
\item<6-> The solution returned is {\color<7>{red}$\epsilon$}-accurate with high probability
\end{itemize}
\end{theorem}
\end{frame}

@@

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
%\color{white}
%\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
%\color{black}
%\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
%\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
%\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
\only<3>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
%\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Implicit threshold level
\end{center}
\begin{itemize}
\item<1-> What if we don't know the threshold level $h$?
\vspace{1em}
\item<2-> Implicitly define $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\vspace{1em}
\item<3-> No existing algorithms for this problem (to our knowledge)
\vspace{1em}
\item<4-> We extend \acl (and its theory!) to this setting
\vspace{1em}
\item<5->\textbf{\iacl} algorithm:
\begin{itemize}
\item<6-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
\item<7-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
\end{itemize}
\end{itemize}
\begin{center}
%\color{white}
%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
%\color{black}
%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

\hspace{-1.9em}
\color{white}
\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
\color{black}
\includegraphics<2>[width=3.78in]{figures/limno_bgape_class_0}
\includegraphics<3>[width=3.78in]{figures/limno_bgape_imp_class_20}
\includegraphics<4>[width=3.78in]{figures/limno_bgape_imp_class_40}
\includegraphics<5>[width=3.78in]{figures/limno_bgape_imp_class_60}
\includegraphics<6>[width=3.78in]{figures/limno_bgape_imp_class_80}
\includegraphics<7>[width=3.78in]{figures/limno_bgape_imp_class_100}
\includegraphics<8>[width=3.78in]{figures/limno_bgape_imp_class_120}
\includegraphics<9>[width=3.78in]{figures/limno_bgape_imp_class_140}
\includegraphics<10>[width=3.78in]{figures/limno_bgape_imp_class_160}
\includegraphics<11>[width=3.78in]{figures/limno_bgape_imp_class_180}
\includegraphics<12>[width=3.78in]{figures/limno_bgape_imp_class_200}
\includegraphics<13>[width=3.78in]{figures/limno_bgape_imp_class_340}
\includegraphics<14->[width=3.78in]{figures/limno_bgape_imp_class_486}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large In our paper, more\ldots
\end{center}
\begin{itemize}
\item<2-> \ldots theory: sample complexity bounds and their proofs in more detail
\item<3-> \ldots applications: estimate world regions of low internet latency\\[0.5em]
\hspace{3em}\includegraphics[height=2in]{figures/map}
\item<4-> \ldots experimental results
\end{itemize}
\end{frame}
%\begin{itemize}
%\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
%      for video chatting, online gaming, etc.?
%\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
%\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1-2>[draft,height=2.5in]{figures/map}
%\color{black}
%\includegraphics<3>[height=2.5in]{figures/map}
%\includegraphics<4>[height=2.5in]{figures/map_ls_150}
%\end{center}
